meeting q

### 2020-11-05 meetingquestions.Rmd
.

Our dependent variables are indexes measured in increments of 0.5, can we use regression methods without making extreme transformations?

@@

model_df5
fit <- lm(model_df5, data = data)
summary(fit)

>>>>

Our dependent variables are indexes measured from 1 to 7. With one being the highest degree of freedom and rights and , can we use regression methods without making extreme transformations?

*subtract mean and divide by sd.*

@@

model_df5
fit <- lm(model_df5, data = data)
summary(fit)
df = matrix(c(predict(fit), data$polrights_fh), ncol = 2)

matplot(df)

plot(predict(fit), data$polrights_fh)
